Unshuffling Permutations

### 2015-09-12 article.tex
reduction

  \begin{proof}[of Claim~\ref{claim:no (nu_2, nu_2)-edge}]
  Combine Claim~\ref{claim:one (nu_1, nu'_1)-edge} together with
  the fact that $\mathcal{M}$ is containment-free.
  \qed
  \end{proof}

@@

  \begin{claim}
    \label{claim:one (nu_1, nu'_2)-edge}
    There is no $(\nu_1, \nu'_2)$-edge in $\mathcal{M}$.
  \end{claim}

  \begin{proof}[of Claim~\ref{claim:one (nu_1, nu'_2)-edge}]
    Suppose, aiming at a contradiction that there is a
    $(\nu_1, \nu'_2)$-edge $(a, a')$ in $\mathcal{M}$.
    According to Claim~\ref{claim:one (nu_1, nu'_1)-edge},
    there exists a $(\nu_1, \nu'_1)$-edge $(b, b')$ in $\mathcal{M}$.
    Since $\mathcal{M}$ is containment-free, we must have $b < a$.
    Then it follows that we have
    $\mu(b) < \mu(a)$ (since $\nu_1$ is increasing) and
    $\mu(b') > \mu(a')$ (since $\nu'_2$ is above $\nu'_2$),
    which contradicts our hypothesis.
    \qed
  \end{proof}

  \begin{claim}
    \label{claim:one (nu'_1, nu'_2)-edge}
    There is no $(\nu'_1, \nu'_2)$-edge in $\mathcal{M}$.
  \end{claim}

  \begin{proof}[of Claim~\ref{claim:one (nu'_1, nu'_2)-edge}]
    Suppose, aiming at a contradiction that there is a
    $(\nu'_1, \nu'_2)$-edge $(a, a')$ in $\mathcal{M}$.
    According to Claim~\ref{claim:one (nu_1, nu'_1)-edge},
    there exists a $(\nu_1, \nu'_1)$-edge $(b, b')$ in $\mathcal{M}$.
    Then it follows that we have
    $\mu(b) < \mu(a)$ (since $\nu_1$ is below $\nu'_1$) and
    $\mu(b') > \mu(a')$ (since $\nu'_1$ is above $\nu'_2$),
    which contradicts our hypothesis.
    \qed
  \end{proof}

@@

  \begin{proof}[of Claim~\ref{claim: all (nu_1, nu'_1)-edges}]
    Suppose, aiming at a contradiction, that
    $\mathcal{M}$ does not contain $N_1$ $(\nu_1, \nu'_1)$-edge.
    Combing Claim~\ref{claim:no (nu_2, nu'_1)-edge} and
    Claim~\ref{claim:no edge below one (nu_2, nu_2)-edge},
    we conclude that there exists a position $a$ in $\nu'_1$ that is
    involded in an edge $(a, a')$ in $\mathcal{M}$ that is
    neither a $\nu_1, \nu'_1)$-edge,
    nor a $(\nu_2, \nu'_1)$-edge,
    nor a $(\nu'_1, \nu'_1)$-edge.
    (In other words, $a' > 2N_1 + N_2$.)
    Furthermore, according to Claim~\ref{claim:one (nu_1, nu'_1)-edge},
    there exists a $(\nu_1, \nu'_1)$-edge in $\mathcal{M}$.
    Then, we have
    $\mu(x) < \mu(a)$ (since $\nu_1$ is below $\nu'_1$) and
    $\mu(x') < \mu(a')$ (since $\nu'_1$ is above any other gadget),
    which contradicts our hypothesis.
    \qed
  \end{proof}

@@

  \begin{claim}
    \label{claim:no (nu_1, nu_3)-edge no (nu'_1, nu_3)-edge}
    There is neither a $(\nu_1, \nu_3)$-edge nor a $(\nu'_1, \nu_3)$-edge
    in $\mathcal{M}$.
  \end{claim}

  \begin{proof}[of Claim~\ref{claim:no (nu_1, nu_3)-edge no (nu'_1, nu_3)-edge}]
    Suppose, aiming at a contradiction, that there exists a
    $(\nu_1, \nu_3)$-edge $(a, a')$ in $\mathcal{M}$.
    According to Claim~\ref{claim:one (nu_1, nu'_1)-edge} there exists
    $(\nu_1, \nu'_1)$-edge $(x, x')$ in $\mathcal{M}$,
    and since $\mathcal{M}$ is containment-free we have $x < a$.
    Therefore, we have
    $\mu(x) < \mu(a)$ (since $\nu_1$ is increasing)
    and
    $\mu(x') > \mu(a')$ (since $\nu'_1$ is above $\nu_3$),
    which contradicts our hypothesis.
    See Fig.~\ref{fig:subfig:no (nu_3, nu'_2)-edge}.

    The same argument shows that there is no
    $(\nu'_1, \nu_3)$-edge in $\mathcal{M}$.
    \qed
  \end{proof}

  \begin{claim}
    \label{claim:no (nu_1, nu_4)-edge}
    There is no $(\nu_1, \nu_4)$-edge in $\mathcal{M}$.
  \end{claim}

  \begin{proof}[of Claim~\ref{claim:no (nu_1, nu_4)-edge}]
    Suppose, aiming at a contradiction, that there exists
    a $(\nu_1, \nu_4)$-edge $(a, b)$ in $\mathcal{M}$.
    According to Claim~\ref{claim:one (nu_1, nu'_1)-edge},
    there exists a $(\nu_1, \nu'_1)$-edge $(x, x')$
    in $\mathcal{M}$.
    Since $\mathcal{M}$ is containment-free, we must have $x < a$.
    Therefore, we have
    $\mu(x) < \mu(a)$ (since $\nu_1$ is incresing)
    and $\mu(x') > \mu(a')$ since $\nu'_1$ is above $\nu_4$),
    which contradicts our hypothesis.
    \qed
  \end{proof}

@@

  \begin{proof}[of Claim~\ref{claim:no (nu_2, nu_4)-edge}]
    Suppose, aiming at a contradiction, that there exists
    a $(\nu_2, \nu_4)$-edge $(a, a')$ in $\mathcal{M}$.
    According to Claim~\ref{claim:one (nu_3, nu'_3)-edge},
    there exists a $(\nu_3, \nu'_3)$-edge $(x, x')$
    in $\mathcal{M}$.
    Since $\mathcal{M}$ is containment-free, we must have
    $x' < a'$.
    Therefore,
    we have $\mu(x) > \mu(a)$ (since $\nu_3$ is above $\nu_4$) and
    $\mu(x') < \nu(a')$ (since $\nu'_3$ is increasing),
    which contradicts our hypothesis.
    \qed
  \end{proof}

@@

  \begin{claim}
    \label{claim:no (nu_4, pi')-edge}
    There is no $(\nu_4, \pi')$-edge in $\mathcal{M}$.
  \end{claim}

  \begin{proof}[of Claim~\ref{claim:no (nu_4, pi')-edge}]
    \qed
  \end{proof}

  \begin{claim}
    \label{claim:no (pi', pi)-edge}
    There is no $(\pi', \pi')$-edge in $\mathcal{M}$.
  \end{claim}

  \begin{proof}[of Claim~\ref{claim:no (pi', pi')-edge}]
    Combine Claim~\ref{claim:one (nu_4, nu'_4)-edge} together with the
    fact that $\mathcal{M}$ is containment-free.
    \qed
  \end{proof}

  \begin{claim}
    \label{claim:no (nu'_3, pi')-edge}
    There is no $(\nu'_3, \pi')$-edge in $\mathcal{M}$.
  \end{claim}

  \begin{proof}[of Claim~\ref{claim:no (nu'_3, pi')-edge}]
    Suppose aiming at a contradiction that there exists
    a $(\nu'_3, \pi')$-edge $(a, a')$ in $\mathcal{M}$.
    Accordint to Claim~\ref{claim:one (nu_3, nu'_3)-edge},
    there exists a $(\nu_3, \nu'_3)$-edge $(b, b')$ in $\mathcal{M}$.
    Then it follows that we have
    $\mu(b) < \mu(a)$ (since $\nu_3$ is below $\nu'_3$) and
    $\mu(b') > \mu(a')$ (since $\nu'_3$ is above $\pi'$),
    which contradicts our hypothesis.
    \qed
  \end{proof}

  Combinf the above claims
\qed
\end{proof}

>>>>

  \begin{proof}[of Claim~\ref{claim:no (nu_2, nu_2)-edge}]
  Combine Claim~\ref{claim:one (nu_1, nu'_1)-edge} with
  the fact that $\mathcal{M}$ is containment-free.
  \qed
  \end{proof}

@@

  \begin{claim}
    \label{claim:no (nu_1, nu'_2)-edge}
    There is no $(\nu_1, \nu'_2)$-edge in $\mathcal{M}$.
  \end{claim}

  \begin{proof}[of Claim~\ref{claim:no (nu_1, nu'_2)-edge}]
    Suppose, aiming at a contradiction that there is a
    $(\nu_1, \nu'_2)$-edge $(a, a')$ in $\mathcal{M}$.
    According to Claim~\ref{claim:one (nu_1, nu'_1)-edge},
    there exists a $(\nu_1, \nu'_1)$-edge $(b, b')$ in $\mathcal{M}$.
    Since $\mathcal{M}$ is containment-free, we must have $b < a$.
    Then it follows that we have
    $\mu(b) < \mu(a)$ (since $\nu_1$ is increasing) and
    $\mu(b') > \mu(a')$ (since $\nu'_2$ is above $\nu'_2$),
    which contradicts our hypothesis.
    \qed
  \end{proof}

  \begin{claim}
    \label{claim:no (nu'_1, nu'_2)-edge}
    There is no $(\nu'_1, \nu'_2)$-edge in $\mathcal{M}$.
  \end{claim}

  \begin{proof}[of Claim~\ref{claim:no (nu'_1, nu'_2)-edge}]
    Suppose, aiming at a contradiction that there is a
    $(\nu'_1, \nu'_2)$-edge $(a, a')$ in $\mathcal{M}$.
    According to Claim~\ref{claim:one (nu_1, nu'_1)-edge},
    there exists a $(\nu_1, \nu'_1)$-edge $(b, b')$ in $\mathcal{M}$.
    Then it follows that we have
    $\mu(b) < \mu(a)$ (since $\nu_1$ is below $\nu'_1$) and
    $\mu(b') > \mu(a')$ (since $\nu'_1$ is above $\nu'_2$),
    which contradicts our hypothesis.
    \qed
  \end{proof}

@@

  \begin{proof}[of Claim~\ref{claim: all (nu_1, nu'_1)-edges}]
    Suppose, aiming at a contradiction, that
    $\mathcal{M}$ does not contain $N_1$ $(\nu_1, \nu'_1)$-edge.
    Combing Claim~\ref{claim:no (nu_2, nu'_1)-edge} and
    Claim~\ref{claim:no edge below one (nu_2, nu'_2)-edge},
    we conclude that there exists a position $a$ in $\nu'_1$ that is
    involded in an edge $(a, a')$ in $\mathcal{M}$ that is
    neither a $(\nu_1, \nu'_1)$-edge,
    nor a $(\nu_2, \nu'_1)$-edge,
    nor a $(\nu'_1, \nu'_1)$-edge.
    (In other words, $a' > 2N_1 + N_2$.)
    Furthermore, according to Claim~\ref{claim:one (nu_1, nu'_1)-edge},
    there exists a $(\nu_1, \nu'_1)$-edge in $\mathcal{M}$.
    Then, we have
    $\mu(x) < \mu(a)$ (since $\nu_1$ is below $\nu'_1$) and
    $\mu(x') < \mu(a')$ (since $\nu'_1$ is above any other gadget),
    which contradicts our hypothesis.
    \qed
  \end{proof}

@@

  \begin{claim}
    \label{claim:no (nu_1, nu_3)-edge no (nu'_1, nu_3)-edge no (nu_1, nu_4)-edge}
    There is neither a $(\nu_1, \nu_3)$-edge nor a $(\nu'_1, \nu_3)$-edge
    nor a $(\nu_1, \nu_4)$-edge
    in $\mathcal{M}$.
  \end{claim}

  \begin{proof}[of Claim~\ref{claim:no (nu_1, nu_3)-edge no (nu'_1, nu_3)-edge no (nu_1, nu_4)-edge}]
    According to Claim~\ref{claim: all (nu_1, nu'_1)-edges},
    all positions in $\nu_1$ and $\nu'_1$ are involved in
    $(\nu_1, \nu'_1)$-edges in $\mathcal{M}$.
    \qed
  \end{proof}

@@

  \begin{proof}[of Claim~\ref{claim:no (nu_2, nu_4)-edge}]
    According to Claim~\ref{claim: all (nu_2, nu'_2)-edges},
    all positions in $\nu_2$ and $\nu'_2$ are involved in
    $(\nu_2, \nu'_2)$-edges in $\mathcal{M}$.
    \qed
  \end{proof}

@@

  \begin{claim}
    \label{claim:no (pi', pi)-edge no (sigma', pi'')-edge no (sigma',sigma'')-edge}
    There is
    neither a $(\pi', \pi')$-edge
    nor a $(\sigma', \pi'')$-edge
    nor a $(\sigma', \sigma'')$-edge
    in $\mathcal{M}$.
  \end{claim}

  \begin{proof}[of Claim~\ref{claim:no (pi', pi)-edge no (sigma', pi'')-edge no (sigma',sigma'')-edge}]
    Combine Claim~\ref{claim:one (nu_4, nu'_4)-edge} with the
    fact that $\mathcal{M}$ is containment-free.
    \qed
  \end{proof}

  Then it follows that that every position in $\sigma$ is involved in
  either a $(\sigma', \nu'_3)$-edge
  or a $(\sigma', \pi')$-edge
  or a $(\sigma', \nu'_4)$-edge
  in $\mathcal{M}$.
  \qed
\end{proof}
